---
title: "An introduction to an R package: CopulaOne"
author: "Lei Hua"
date: "October 21, 2016"
output: html_document
---

The R package *CopulaOne* implements basic functions, such as, cdf and pdf for a bivariate copula that is very flexible and parsimonious. Compared to those of the other bivariate parametric copula families, the main merits of the bivariate copula is that, it can account for full-range tail dependence in both upper and lower tails, and the upper and lower tails can be either symmetric or asymmetric.

## Installation
The R package CopulaOne can be easily installed from github by the following two lines.
```{r}
library(devtools)
install_github("larryleihua/CopulaOne")
```


```{r}
library(CopulaOne)
```

Simulation based on the copula can be done follows:

```{r, echo=FALSE}
library(CopulaOne)
UU = rGGEE_COP(10, a=0.5, b=0.8)
```

Joint density, cdf functions can be derived as
```{r}
den <- dGGEE_COP(0.2, 0.3, 1.2, 0.5)
cdf <- pGGEE_COP(0.2, 0.3, 1.2, 0.5)
cat("The copula density and cdf are:", den, cdf, "\n")
```

Contour plots can be plotted directly for a given copula as follows.
```{r fig.width=11, fig.height=6, echo=FALSE}
layout(matrix(c(1,2),1,2))
plotCopulaOne(1.2, 0.5, marg = "normal")
plotCopulaOne(1.2, 0.5, marg = "uniform")
```



